\Title

### 2021-06-25 manuscript/content.tex

With the goal of highlighting the importance of randomizing the order in which
the overlapping windows are iterated, we interpolated the airborne synthetic
survey using the same estimated values for the \emph{damping} and
\emph{depth} but disabling the random shuffling of the windows, iterating over
them in sequential order.
Fig.~\ref{fig:eql-boost-airborne}c shows the differences between the target
grid and the predictions made by the gradient-boosted equivalent sources
without random shuffling the windows.
Fig.~\ref{fig:eql-boost-airborne}d shows the RMS error of the
residuals after each iteration.
These results show how the gradient-boosted equivalent sources underperform by
iterating over the overlapping windows in sequential order: they fail to
produce realistic and accurate predictions while the speed in which the
algorithm converges is considerable smaller.

@@

Finally, the results in Fig.~\ref{fig:eql-boost-airborne} highlight the
importance of randomize the order in which the overlapping windows are
iterated.
Running the gradient boosting process by sequentially iterating over the
overlapping windows produce predictions of considerable lower quality with
a much smaller convergence rate than the ones obtained by a previous random
shuffling of the windows.

@@

Gradient-boosted equivalent sources were shown to heavily reduce the computer
memory needed to estimate source coefficients, making it possible to
interpolate large datasets with millions of points that would otherwise produce
Jacobian matrices larger than the available memory.
The interpolations obtained though this new method achieve close to the same
accuracy than the regular equivalent sources, while reducing the computation
time needed to estimate the source coefficients by approximately three times.
We also show that an overlap of 50\% between adjacent windows achieves a good
compromise between accuracy and computation time.
The size of the overlapping windows should be chosen as the maximum value
possible that creates Jacobian matrices that still fit into computer memory.
Moreover, randomizing the order in which the overlapping windows are iterated
is highly recommended to improve the quality of the predictions and increasing
the convergence rate of the algorithm.

>>>>

With the goal of highlighting the importance of randomizing the order in which
the overlapping windows are iterated, we interpolated the airborne synthetic
survey using the same estimated values for the \emph{damping} and
\emph{depth} but disabling the random shuffling of the windows, iterating over
them in sequential order.
Fig.~\ref{fig:eql-boost-airborne}c shows the differences between the target
grid and the predictions made by the gradient-boosted equivalent sources
without random shuffling the windows.
Fig.~\ref{fig:eql-boost-airborne}d shows the RMS error of the
residuals after each iteration.
These results show how the gradient-boosted equivalent sources underperform by
iterating over the overlapping windows in sequential order: they fail to
produce realistic and accurate predictions while the speed in which the
algorithm converges is smaller.

@@

Finally, the results in Fig.~\ref{fig:eql-boost-airborne} highlight the
importance of randomizing the order in which the overlapping windows are
iterated.
Running the gradient boosting algorithm sequentially produces less accurate 
predictions and decreases the convergence rate.

@@

Gradient-boosted equivalent sources were shown to heavily reduce the computer
memory needed to estimate source coefficients, making it possible to
interpolate large datasets with millions of points that would otherwise produce
Jacobian matrices larger than the available memory.
The interpolations obtained though this new method achieve close to the same
accuracy than the regular equivalent sources, while reducing the computation
time needed to estimate the source coefficients by approximately three times.
We also show that an overlap of 50\% between adjacent windows achieves a good
compromise between accuracy and computation time.
The size of the overlapping windows should be chosen as the maximum value
possible that creates Jacobian matrices that still fit into computer memory.
Moreover, randomizing the order in which the overlapping windows are iterated
is essential to improve the quality of the predictions and increase
the convergence rate of the algorithm.
